A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-07 main.tex
Keywords

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous,screen]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=true}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003521.10003525</concept_id>
<concept_desc>Social and professional topics~History of programming languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

@@

In this paper we have introduced a calculus to compute commutating operations on
intersections of regular languages that we call \Calculus{}. We have evaluated
it on \NrBenchmarks{} Parikh automata intersection problems generated by the
\OstrichPlus{} string solver \cite{ostrich-plus} solving the PyEx benchmark
suite \cite{pyex} using our Parikh automata solver \Catra.

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous,screen]{acmart}\settopmatter{printfolios=true,printccs=true,printacmref=true}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10003752.10003766.10003773.10003775</concept_id>
  <concept_desc>Theory of computation~Quantitative automata</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10003752.10003766.10003776</concept_id>
  <concept_desc>Theory of computation~Regular languages</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10003752.10003790.10003794</concept_id>
  <concept_desc>Theory of computation~Automated reasoning</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10003752.10010124.10010138.10010142</concept_id>
  <concept_desc>Theory of computation~Program verification</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10003752.10003790.10011192</concept_id>
  <concept_desc>Theory of computation~Verification by model checking</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  </ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Quantitative automata}
\ccsdesc[300]{Theory of computation~Regular languages}
\ccsdesc[500]{Theory of computation~Automated reasoning}
\ccsdesc[300]{Theory of computation~Program verification}
\ccsdesc[300]{Theory of computation~Verification by model checking}
%% End of generated code

@@

In this paper we have introduced a calculus to compute commutating operations on
intersections of regular languages that we call \Calculus{}. We have evaluated
it on \NrBenchmarks{} Parikh automata intersection problems generated by the
\OstrichPlus{} string solver \cite{ostrich-plus} solving the PyEx benchmark
suite \cite{pyex} using our Parikh automata solver \Catra{}.
